Quantitative Benchmarking for Automatically Generated Conjectures

### 2017-09-07 TEBenchmarkPaper/article.tex
Add basic intro

% Maybe lay out argument in bullet points; flesh out sentences later

>>>>

% Maybe lay out argument in bullet points; flesh out sentences later
Automated \emph{theory exploration} (ATE), also known as
\emph{conjecture generation/formation}, is the open-ended problem of producing
conjectures about a given logical theory which are somehow ``interesting''.

This has applications wherever we find use for formal statements: for example in
proof assistants and their libraries, in mathematics education and research, and
(especially for our purposes) in the specification, verification, optimisation
and testing of software.

Existing attempts at tackling this problem are difficult to compare and study,
due partially to the variety of approaches taken, but also because of the
inherent ambiguity of the task and the different goals emphasised by the authors
and their evaluation methods.

Our contributions include:

\begin{itemize}
\item A general methodology for benchmarking ATE systems.
\item Resolving the issue of ``interestingness'' through the use theorem-proving
  benchmarks as a ground-truth.
\item A specific instantiation of this methodology, using the Tons of Inductive
  Problems benchmark as a corpus.
\item Automated tooling to produce and analyse this benchmark, translating to
  Haskell and Isabelle code for the QuickSpec and IsaCoSy systems, respectively.
\end{itemize}

Section \ref{sec:background} describes the ATE problem in more detail, along
with existing approaches and their evaluation methodologies. We explain our
proposal for a more general benchmark in section \ref{section:proposal} and
section \ref{application} shows the results when applied to existing ATE tools.
Analysis of these results is given in section \ref{section:discussion} and
concluding remarks in \ref{section:conclusion}.
